%% start of file `rnegron_resume.tex'.
%% Original template copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\documentclass[11pt,a4paper,sans]{moderncv}

% moderncv themes
\moderncvstyle{classic}
\moderncvcolor{grey}

% adjust the page margins
\usepackage[scale=0.9]{geometry}

\renewcommand*{\namefont}{\fontsize{40}{10}\mdseries\upshape}

% personal data
\name{Ra\'ul}{Negr\'on}
\email{raul.esteban.negron@gmail.com}
\homepage{raulnegron.me}
\social[linkedin]{raulnegron}
\social[github]{rnegron}


%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}

%-----       resume       ---------------------------------------------------------
\makecvtitle

\vspace*{-6mm}

\section{Experience}
\subsection{Industry}

\cventry{2020-Present}{Software Engineer}{BrainHi}{San Juan}{Puerto Rico}{\begin{itemize}
  \item Led an overhaul of the backend logic for conversations, from ideation to development and release.
  \item Added fullstack support for inbound and outbound Multimedia Messaging Service (MMS) based texting.
  \item Built integrations with EHR services, as well as Slack and Salesforce integrations to support internal teams.
 \item Developed the frontend and backend for a schedulable Messaging Campaign feature (bulk messaging).
  \item Built a wallet-like solution that handles in-product purchases of credits for use in Messaging Campaigns.
\end{itemize}}
\medskip

\cventry{2019-2020}{Full-stack Developer}{Alias Payments}{Guaynabo}{Puerto Rico}{\begin{itemize}
  \item Implemented a payout system for automatically transferring thousands of dollars daily.
  \item Integrated referral codes into the promotions backend.
\item Designed and built APIs, internal systems and client-facing features using Node.js and Ember.js.
  \item Managed Amazon Web Services infrastructure, in accordance with  PCI DSS requirements.
\end{itemize}}
\medskip

\cventry{2018-2019}{Junior Back-end Developer}{Abartys Health}{Guaynabo}{Puerto Rico}{\begin{itemize}
\item Improved, tested and maintained an API backed by the Django REST framework.
\item Integrated Amazon Web Services such as Lambda, ECS, SNS and SQS, following best practices for each.
\item Performed MySQL database optimizations, migrations and maintenance on AWS RDS.
\item Managed the transition to a CI/CD development workflow using Docker and AWS CodePipeline.
\end{itemize}
}
\medskip

\cventry{2017-2018}{Intern}{National Institute of Standards and Technology}{Gaithersburg}{Maryland}{\begin{itemize}
\item Implemented a Flask-based RESTful API for parsing form data into batch file data.
\end{itemize}}
\medskip

%\cventry{2016}{Full Stack Developer Intern}{University of Puerto Rico}{San Juan}{Puerto Rico}{Managed technical aspects of the web portal for Umbral Magazine (\url{http://umbral.uprrp.edu/}). Worked on the Drupal backend, implementing security measures server side and performing regular maintenance. Optimized MySQL database, lowering its size by around 80\% and improving its performance by around 50\%.}
%\medskip


% \subsection{Academia}
% \cventry{2014--2015}{Undergraduate Researcher}{University of Puerto Rico}{San Juan}{Puerto Rico}{Performed undergraduate research work in mathematics on a project titled "Exact divisibility of exponential sums associated to elementary symmetric Boolean functions". This NSF and CURM-sponsored research culminated in several oral and poster presentations which took place in Los Angeles, California and San Antonio, Texas.}
% \medskip

\section{Relevant Skills}
\cvitem{}{Proficiency in Python and JavaScript.}{}
\cvitem{}{Experience with Django, Node.js, TypeScript, React and Amazon Web Services.}{}
\cvitem{}{Experience working with UNIX-like systems, RESTful APIs, Git, Docker, Terraform, SQL and MongoDB.}{}
\medskip

\section{Education}
\cventry{Aug 2013 - Feb 2018\hspace{.2cm}}{B.Sc. in Computer Science}{University of Puerto Rico at R\'io Piedras}{}{\textit{3.8 Overall GPA}}{}
\medskip

\section{Relevant Courses}
\cvitem{}{Data Structures, Algorithms, Databases, Discrete Mathematics, Linear Algebra, Abstract Algebra, Theory of Computation}{}

% \section{Activities}
% \cventry{2016}{Teaching Assistant for High Level Programming Languages, Spring 2016}{Provided tutoring and weekly office hours for students. Helped design and grade coursework on functional programming}{}{}{}{}
% \medskip

\section{Awards and Certifications}

\cventry{2014--2017}{Claude Shannon Scholar}{Received the Claude Shannon scholarship for excellence in Computer Science and Mathematics for three years consecutively}{}{}{}
\medskip


%\section{Awards}
\section{Languages}
\cvitemwithcomment{Spanish}{Native}{}
\cvitemwithcomment{English}{Fluent}{}

\clearpage
\end{document}
%% end of file `rnegron_resume.tex'.
